Summary of cell type ontologies in reference files

### 2024-12-12 analyses/cell-type-consensus/exploratory-notebooks/01-reference-exploration.Rmd
add some headers for tables

```{r}
print_df <- lca_df |> 
  dplyr::select(blueprint_annotation_main, blueprint_annotation_fine, panglao_annotation, total_lca, cl_annotation)

@@

@@

@@

@@

@@

@@

@@

@@

```{r}
lca_df |> 
  dplyr::filter(total_lca > 1) |> 
  dplyr::select(cl_annotation, total_descendants) |> 
  unique()
```

@@

@@

>>>>

#### Blood cell

```{r}
print_df <- lca_df |> 
  dplyr::select(blueprint_ontology, blueprint_annotation_main, blueprint_annotation_fine, panglao_ontology, panglao_annotation, total_lca, lca, cl_annotation)

@@

#### Bone cell

@@

#### Myeloid leukocyte

@@

#### Progenitor cell

@@

#### Lining cell

@@

#### Supporting cell

@@

### Discarded cell types

@@

#### Neuron

@@

```{r}
lca_df |> 
  dplyr::filter(total_lca > 1) |> 
  dplyr::select(cl_annotation, total_descendants) |> 
  unique() |>
  dplyr::arrange(total_descendants)
```

@@

#### Hematopoietic precursor cell

@@

#### Perivascular cell
